---
title: "2-15-18 Stapleton qPCR"
author: "Thomas Billman"
output: html_document
---
##Loading packages
If you do not already have the qpcR library installed in your R, please uncomment the top line and install before running the rest of the code.
```{r}
#install.packages("qpcR")
library(qpcR)
```
##Reading in data
I added this data to my Github so that this code can be run from other machines with internet connections. 
```{r}
hex <- read.csv(file = url("https://raw.githubusercontent.com/tbillman/Stapleton-Lab/master/qpcR/2-13-18/Stapleton%20Test%202.13.18%20HEX.csv"))
```
##Starting with the Analysis
This is where I generate the models for all of the runs included. 
```{r include = FALSE}
m <- modlist(x = hex, cyc = 1, model = l4, remove = "none")
```
Calculating the efficiencies of all the models
```{r}
heff = lapply(m,function(x){
  efficiency(x,plot = FALSE)
})
```
This is where we explicitly extract the critical points of the first and second derivatives of the models
```{r}
hcpd1 = vector(); hcpd1 = lapply(1:length(heff),function(x){
  hcpd1 = c(hcpd1, heff[[x]]$cpD1)
})
hcpd1 = unlist(hcpd1)

hcpd2 = vector(); hcpd2 = lapply(1:length(heff),function(x){
  hcpd2 = c(hcpd2, heff[[x]]$cpD2)
})
hcpd2 = unlist(hcpd2)
```
##Generating output
```{r}
eff.frame = as.data.frame(rbind(hcpd1,hcpd2))
colnames(eff.frame) = colnames(hex)[-1]; rownames(eff.frame) = c("cpD1","cpD2")
write.csv(eff.frame, file= "C:/Users/Thomas/Documents/GitHub/Stapleton-Lab/qpcR/2-13-18/EffDat.csv")
```